Subset coercions in \Coq

### 2006-05-04 papers/article/main.tex
Fix wf macro and add werner ref

Some basic properties of this system are well-formedness of
environments: if $`G \typed t : T$ then $\typedwf `G$ and
well-sortedness: if $`G \typed t : T$ then $T = \Type$ or $`G \typed T :
s$.

@@

\begin{lemma}[Weakening]
  Suppose $\typedwf `G, x : S, `D$.
  If $`G, `D \typed t : T$ then $`G, x : S, `D \typed t : T$. 
  If $`G, `D \typed T \sub U : s$ then $`G, x : S, `D \typed T \sub U : s$.
\end{lemma}
\begin{proof}
  Straightforward mutual induction.
\end{proof}

@@

Our interpretation will build a full-fledged \CCI term from its
algorithmic skeleton and a rich type written in \Russell. Obviously, we
cannot infer proof terms where they are needed in \CCI, but we can build
a \emph{partial} term, leaving typed holes where proofs are
needed. Hence we add a rule to build existential variables (or
metavariables) to the target calculus ($\typeq$ denotes the new system's typing judgement):
\begin{prooftree}
  \UAX{}
  {$`G \typeq P : \Prop$}
  {$`G \typeq ?_{P} : P$}
  {}
\end{prooftree}

@@

The proof of this proposition is the main technical contribution of this
paper. It also represented the main difficulty in our work. 
The remainder of this section is organized as follows: first we will
define the explicit coercion derivation algorithm which will permit to
put proof obligations in the terms, then we will define the
interpretation of terms which is mutually recursive with the first
one. Finaly we will present a proof sketch of the aforementionned
proposition.

>>>>

Some basic properties of this system are well-formedness of
environments: if $`G \typed t : T$ then $\wf{`G}$ and
well-sortedness: if $`G \typed t : T$ then $T = \Type$ or $`G \typed T :
s$.

@@

\begin{lemma}[Weakening]
  Suppose $\wf{`G, x : S, `D}$.
  If $`G, `D \typed t : T$ then $`G, x : S, `D \typed t : T$. 
  If $`G, `D \typed T \sub U : s$ then $`G, x : S, `D \typed T \sub U : s$.
\end{lemma}
\begin{proof}
  Straightforward mutual induction.
\end{proof}

@@

Our interpretation will build a full-fledged \CCI term from its
algorithmic skeleton and a rich type written in \Russell. Obviously, we
cannot infer proof terms where they are needed in \CCI, but we can build
a \emph{partial} term, leaving typed holes where proofs are
needed. Hence we add a rule to build existential variables (or
metavariables) in the target calculus ($\typeq$ denotes the new system's typing judgement):
\begin{prooftree}
  \UAX{}
  {$`G \typeq P : \Prop$}
  {$`G \typeq ?_{P} : P$}
  {}
\end{prooftree}

@@

The proof of this proposition is the main technical contribution of this
paper. It also represented the main difficulty in our work. 
The remainder of this section is organized as follows: first we will
define the explicit coercion derivation algorithm which will permit to
put proof obligations in the terms, then we will define the
interpretation of terms which is mutually recursive with the precedent
algorithm. Finaly we will present a proof sketch of the aforementionned
proposition.
